Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-10-02 paper.tex
Updated Paper
Numeric index fix.
Updated Equation
Golden Ratio Equation Fix

\begin{document}
\title{Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)}
%

@@

        Based on the historically best candidate
        solution and the elite set, we use the Golden Ratio (shown in
        Figure~\ref{fig.golden_ratio}) to compute the distance between new individuals
        in the population, making an improved distribution. It randomly selects a
        solution from the elite set and uses the Golden Ratio 
        \cite{nematollahi2020novel, gaikwad2021face, khesin2022golden, sym13081334, https://doi.org/10.1111/nyas.14895} 
        to compute multiple solutions against the best-found candidate.

        \begin{figure}
            \centering
            \includegraphics[width=25mm]{img/fig_golden_ratio.pdf}
            \caption{Golden Ratio equation.} \label{fig.golden_ratio}
            \end{figure}

>>>>

\begin{document}
\title*{Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)}
%

@@

        Based on the historically best candidate
        solution and the elite set, we use the Golden Ratio (shown in
        Equation~\ref{eq.golden_ratio}) to compute the distance between new individuals
        in the population, making an improved distribution. It randomly selects a
        solution from the elite set and uses the Golden Ratio 
        \cite{nematollahi2020novel, gaikwad2021face, khesin2022golden, sym13081334, https://doi.org/10.1111/nyas.14895} 
        to compute multiple solutions against the best-found candidate.

        \begin{equation}
            \centering
            \begin{matrix}\includegraphics[width=25mm]{img/eq_golden_ratio.pdf}\end{matrix}
            \label{eq.golden_ratio}
            \end{equation}
